\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-03-02 manuscript/paper.tex
Minor update

  \node[rectangle, inner sep=8mm,draw=black!130, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.4cm, xshift=-8cm]{\Large$\bm{k = 1, \ldots,K}$}}] at (6.5,0.4) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick, label={[anchor=west, yshift=-0.5cm, xshift=-2.7cm]{\Large$\bm{l = 1, \ldots,L}$}}] {};

@@

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-independent}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (5,2.8) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-to-event}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (11.5,2.8) {};

>>>>

  \node[rectangle, inner sep=8mm,draw=black!130, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.4cm, xshift=-8cm]{\Large$\bm{k = 1, \ldots,K}$}}] at (7,0.4) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick, label={[anchor=west, yshift=-0.5cm, xshift=-2.7cm]{\Large$\bm{l = 1, \ldots,L}$}}] {};

@@

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-independent}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (5.5,2.8) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-to-event}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (12,2.8) {};
